\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-19 chapters/2_rel_work.tex
Merge comments from Constantin and Steffen

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for joint segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
% encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}. % Semi-convolutiona: \cite{novotny2018semi}
% \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}.
%  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}

@@

\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts. 
Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters. 
% \TODO{Roman, Cocoons, Benjamin?}
The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HC linkage criteria, e.g. average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a neural network \cite{nunez2013machine,knowles2016rhoananet}.

\textbf{Clustering of signed graphs} has the goal of partitioning a graph with both attractive and repulsive cues. Finding an optimally balanced partitioning has a long history in combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy heuristic algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
% \TODO{Cannot-link constraints?}
% Missing: Funke proposals, discussion about cannot-link constraints!!!

This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a generalized framework and adopt ideas from the proposal-free methods \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict long-range relationships between pixels.

>>>>

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
% encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}. % Semi-convolutiona: \cite{novotny2018semi}
% \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}.
%  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}

@@

\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts. 
Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters. 
% \TODO{Roman, Cocoons, Benjamin?}
The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HC linkage criteria, e.g. average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a random forest classifier \cite{nunez2013machine,knowles2016rhoananet}.

\textbf{Clustering of signed graphs} has the goal of partitioning a graph with both attractive and repulsive cues. Finding an optimally balanced partitioning has a long history in combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
% \TODO{Cannot-link constraints?}
% Missing: Funke proposals, discussion about cannot-link constraints!!!

This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a generalized framework and adopt ideas from the proposal-free methods \cite{liu2018affinity,wolf2018mutex,lee2017superhuman} to predict long-range relationships between pixels.

### 2019-05-19 chapters/3_algorithm.tex
Merge comments from Constantin and Steffen

Apart from the linkage criteria defined in Table \ref{tab:linkage-criteria}, additional ones were proposed in the literature:
\cite{nunez2013machine} for example uses a learned approach where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas 
\cite{funke2018large} uses a \emph{quantile} linkage criteria by populating a histogram for each inter-cluster interaction. In our experiments, we decided to focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most common options.

>>>>

Apart from the linkage criteria defined in Table \ref{tab:linkage-criteria}, additional ones were proposed in the literature:
\cite{nunez2013machine} for example uses a learned approach where a random forest classifier updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas 
\cite{funke2018large} uses a \emph{quantile} linkage criteria by populating a histogram for each inter-cluster interaction. In our experiments, we decided to focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most common options.

### 2019-05-19 chapters/supplementary.tex
Merge comments from Constantin and Steffen

\paragraph*{Complexity} In the main loop, the algorithm iterates over all edges, but the only iterations presenting a complexity different from $\mathcal{O}(1)$ are the ones involving a merge of two clusters, which are at most $N-1$. By using a union-find data structure (with path compression and union by rank) the time complexity of \texttt{merge}$(u, v)$ and \texttt{find}($u$) operations is $\mathcal{O}(\alpha(N))$, where $\alpha$ is the slowly growing inverse Ackerman function. The algorithm then iterates over the neighbors of the merged cluster (at most $N$) and updates/deletes values in the priority queue ($\mathcal{O}(\log |E|)$). Therefore, similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$. In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory and does not scale up well. Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$. 
% and \UPDATE{in Fig. \ref{fig:runtime_plot} we show how the empirical runtime of \algname{} is much closer to $\mathcal{O}(N \log N)$ than $\mathcal{O}(N^2 \log N)$.} 
With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$. 
Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity. \TODO{Empirical complexity plot?}

@@

\begin{prop} \label{prop:equiv_MWS}
The Mutex Watershed Algorithm \ref{alg:mutex_watershed} (MWS) with empirical $\mathcal{O}(N \log N)$ complexity introduced by \cite{wolf2018mutex} returns the same final clustering given by the \algname{} Algorithm \ref{detailed_alg} with the use of cannot-link constraints and an Absolute Maximum update rule:
\begin{equation}\label{eq:def_abs_max}
f_{\mathrm{Abs.Max.}}(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
            \tilde{\cost}_2 & \text{otherwise}
             \end{cases} 
\end{equation}
\end{prop}
\begin{proof}
Both algorithms sort edges in descending order of the absolute interactions $|w_e|$ and then iterate over all of them. The only difference is that MWS, after merging two clusters, does not update the interactions between the new cluster and its neighbors. 
However, since with an Abs. Max. linkage the interaction between clusters is simply given by the edge with highest absolute weight $|w_e|$, the order by which edges are iterated over in \algname{} is never updated. Thus, both algorithms perform precisely the same steps and return the same clustering.
\end{proof}
\begin{prop}
The \algname{} Algorithm \ref{detailed_alg} with the Absolute Maximum linkage defined in Eq. \ref{eq:def_abs_max} returns the same final clustering whether or not cannot-link constraints are enforced. 
\end{prop}
\begin{proof}
% In Proposition \ref{prop:equiv_MWS} we observed that \algname{} with Abs. Max. linkage never updates the order by which edges are iterated over
In the \algname{} Algorithm \ref{detailed_alg}, the clustering is updated only when two clusters are merged and the condition at line 9 is satisfied. 
We also observe that, in the unconstrained version of \algname{}, the predicate \texttt{canBeMerged} at line 9 can never be false.
Let us now contradict the initial hypothesis and assume by absurd that the constrained version of \algname{} introduces a cannot-link constraints between two clusters sharing a positive interaction $\tilde{w}>0$ and outputs a different clustering as compared to the unconstrained version. 
This can happen only in the situation \TODO{shown in Fig. \ref{fig:contradiction_case}}, when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$. 
Then, according to Eq. \ref{eq:def_abs_max}, the new merged cluster $uv$ and $t$ are constrained and share a positive interaction. 
But this case can never happen, since if $|w_{vt}|>|w_{ut}|$ then clusters $v$ and $t$ are merged before clusters $u$ and $t$ are constrained.  
\end{proof}

>>>>

\paragraph*{Complexity} In the main loop, the algorithm iterates over all edges, but the only iterations presenting a complexity different from $\mathcal{O}(1)$ are the ones involving a merge of two clusters, which are at most $N-1$. By using a union-find data structure (with path compression and union by rank) the time complexity of \texttt{merge}$(u, v)$ and \texttt{find}($u$) operations is $\mathcal{O}(\alpha(N))$, where $\alpha$ is the slowly growing inverse Ackerman function. The algorithm then iterates over the neighbors of the merged cluster (at most $N$) and updates/deletes values in the priority queue ($\mathcal{O}(\log |E|)$). Therefore, similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$. In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory. Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$. 
% and \UPDATE{in Fig. \ref{fig:runtime_plot} we show how the empirical runtime of \algname{} is much closer to $\mathcal{O}(N \log N)$ than $\mathcal{O}(N^2 \log N)$.} 
With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$. 
Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity. \TODO{Empirical complexity plot?}

@@

\begin{prop} \label{prop:equiv_MWS}
The Mutex Watershed Algorithm \ref{alg:mutex_watershed} (MWS) with empirical $\mathcal{O}(N \log N)$ complexity introduced by \cite{wolf2018mutex} returns the same final clustering given by the \algname{} Algorithm \ref{detailed_alg} with the use of cannot-link constraints and an Absolute Maximum update rule:
\begin{equation}\label{eq:def_abs_max}
f_{\mathrm{Abs.Max.}}(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
            \tilde{\cost}_2 & \text{otherwise}
             \end{cases} 
\end{equation}
\end{prop}
\begin{proof}
Both algorithms sort edges in descending order of the absolute interactions $|w_e|$ and then iterate over all of them. The only difference is that MWS, after merging two clusters, does not update the interactions between the new cluster and its neighbors. 
However, since with an Abs. Max. linkage the interaction between clusters is simply given by the edge with highest absolute weight $|w_e|$, the order by which edges are iterated over in \algname{} is never updated. Thus, both algorithms perform precisely the same steps and return the same clustering.
\end{proof}
\begin{prop}
The \algname{} Algorithm \ref{detailed_alg} with the Absolute Maximum linkage defined in Eq. \ref{eq:def_abs_max} returns the same final clustering whether or not cannot-link constraints are enforced. 
\end{prop}
\begin{proof}
% In Proposition \ref{prop:equiv_MWS} we observed that \algname{} with Abs. Max. linkage never updates the order by which edges are iterated over
In the \algname{} Algorithm \ref{detailed_alg}, the clustering is updated only when two clusters are merged and the condition at line 9 is satisfied. 
We also observe that, in the unconstrained version of \algname{}, the predicate \texttt{canBeMerged} at line 9 can never be false because cannot-link constraints are never introduced at line 14.
Let us now contradict the initial hypothesis and assume by absurd that the constrained version of \algname{} introduces a cannot-link constraints between two clusters sharing a positive interaction $\tilde{w}>0$ and outputs a different clustering as compared to the unconstrained version. 
This can happen only in the situation \TODO{shown in Fig. \ref{fig:contradiction_case}}, when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$. 
Then, according to Eq. \ref{eq:def_abs_max}, the new merged cluster $uv$ and $t$ are constrained and share a positive interaction. 
But this case can never happen, since if $|w_{vt}|>|w_{ut}|$ then clusters $v$ and $t$ are merged before clusters $u$ and $t$ are constrained.  
\end{proof}
